Formale Grundlagen der Informatik I \\\large{ Abgabe der Hausaufgaben } \\\large{ Übungsgruppe 24 am \today }

### 2015-05-21 FGI/FGI W7/fgi_w7_v1.tex
task structure
automaton task 6.4.1

\begin{document}
	\maketitle
	\newpage

\end{document}

>>>>

\begin{document}
	\maketitle
	\newpage
	\section*{Aufgabe 6.4}
	\label{sec:a6.4}
	\subsection*{Aufgabe 6.4.1}
	\label{ssec:a6.4.1}
	\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3.0cm,semithick]
		\node [initial, state]		(A)					{$z_1$};
		\node [state]				(B) [right of=A]	{$z_2$};
		\node [state]				(C) [right of=B]	{$z_3$};
		\node [accepting, state]	(D) [right of=C]	{$z_4$};
		\node [state]				(E) [right of=D]	{$z_{ERR}$};

		\path
			(A) edge [loop above]		node [align=left]	{$a,\perp|\perp$}						(A)
			(A) edge					node [align=left]	{$b,\perp|b\perp$}						(B)
			(A) edge [bend right=30]	node [align=left]	{$\lambda,\perp|\perp$}					(D)
			(B) edge [loop above]		node [align=left]	{$b,b|B$ \\ $b,B|bB$}					(B)
			(B) edge					node [align=left]	{$a,B|\lambda$}							(C)
			(B) edge [bend right=30]	node [align=left]	{$a,b|\lambda$}							(E)
			(C) edge [loop above]		node [align=left]	{$a,B|\lambda$}							(C)
			(C) edge					node [align=left]	{$\lambda,\perp|\perp$} 				(D)
			(D) edge					node [align=left]	{$b,\perp|\perp$ \\ $a,\perp|\perp$}	(E)
		;
	\end{tikzpicture}
	\subsection*{Aufgabe 6.4.2}
	\label{ssec:a6.4.2}
	%-------------------------------------------------%
	\newpage
	\section*{Aufgabe 6.5}
	\label{sec:a6.5}
	\subsection*{Aufgabe 6.5.1}
	\label{ssec:a6.5.1}
	\subsection*{Aufgabe 6.5.2}
	\label{ssec:a6.5.2}
	\subsection*{Aufgabe 6.5.3}
	\label{ssec:a6.5.3}
	%-------------------------------------------------%
	\newpage
	\section*{Aufgabe 6.5}
	\label{sec:a6.5}
\end{document}
